Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: significant improvement in the dark energy figure of merit

### 2017-09-27 Draft/Draft1.3.tex
minor changes

%\altaffiltext{1}{xiaodongli@kias.re.kr}
%\altaffiltext{2}{cbp@kias.re.kr}
%\altaffiltext{3}{csabiu@kasi.re.kr}
%\altaffiltext{4}{\bf Hyunbae: your email}
\altaffiltext{1}{Corresponding Author: kjhan@kias.re.kr}

@@

\begin{abstract}
We use the anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
%Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
%while improving upon earlier works \citep{Li2016},
%we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
%This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
%allowing for competitive and unbiased constrains to be placed on cosmological parameters.
The Alcock-Paczynski (AP) test was performed via the redshift dependence of clustering on scales of 6-40 $h^{-1}\rm Mpc$.
We improve the methodology of \cite{Li2016} by significantly reducing its computation time. 
This enables us to efficiently explore three or more cosmological parameters.
We then apply the improved method on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$.
In combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, we obtain
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results 
reduces the error bars by $\sim$30-40\%,
%and reduces the area of $w_0-w_a$ contour by 50\%.
and improves the dark energy figure of merit by a factor of 2. 
We checked the robustness of the results.
%The AP method may %be combined with the standard BAO method,
%greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

@@

\begin{figure*}
   \centering{
   \includegraphics[height=5cm]{fig_xy.eps}
   %\includegraphics[height=8cm]{fig4_1.eps}
   %\includegraphics[height=7cm]{FVol.eps}
   %\includegraphics[height=8cm]{xy.eps}
   %\includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_xy}
   The distance dependence of the shape distortion in four wrongly assumed cosmologies.
   Assuming a true cosmology of $\Omega_m=0.31$, $w=-1$.
   There are four perfect squares with their true shapes plotted in blue dashed lines.
   They are measured by an observer located at the origin, and the distances are reprojected in the four wrong cosmologies.
   The apparently distorted shapes are plotted in red solid lines.
   }
\end{figure*}

@@

In recent years the Alcock-Paczynski (AP) test \citep{AP1979} applied to galaxy redshift samples \citep{Outram2004,Blake2011,Alam2016}, 
has allowed tight constraints to be placed on the background averaged distance scales, $D_A(z)$ and $H^{-1}(z)$.  
Assuming an incorrect cosmological model for the coordinate transformation between redshift space and comoving space
produces residual geometric distortions in the resultant galaxy distribution (see  Fig.\ref{fig_xy}). 
These distortions are induced by the fact that measured distances along 
and perpendicular to the line of sight are connected with cosmological parameters differently. 
Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.

@@

Previously, we proposed to use the {\it redshift dependence} of the AP distortion\cite{Li2014} as a way of mitigating the RSD effect. The clustering anisotropies produced by RSD are, although large, close to uniform in magnitude over a wide range in redshift.  However, if cosmological parameters are incorrectly chosen resulting in an AP effect, 
the anisotropy in the clustering signal has a clear redshift dependence
(as an illustration, Fig.\ref{fig_xy} shows how the shape distortion of objects varies with distance (i.e., redshift) 
when incorrect cosmologies are used to infer distances).
In a later work\cite{Li2015}, we developed an AP methodology 
that utilizes the redshift dependence of the galaxy 2-point correlation function (2pCF), 
measured as a function of angle between the galaxy pair and line-of-sight (LoS).

@@

The CPL parametrization has many obvious advantages, for instance, a manageable parameter space, 
the bounded behavior at high redshift, 
and the ability to accurately reconstruct many dark energy theories\cite{CPL_L}. 
So it was widely used in the literature to reconstruct dark energy from observations.
The constraining power is usually quantified by the DETF (Dark Energy Task Force) \cite{DETF} figure of merit, 
defined as the reciprocal of the area of the error ellipse enclosing the 95\% confidence limit (CL) in the $w_0-w_a$ plane. 
Fig.\ref{fig_xy} shows that redshift dependence of shape distortion is sensitive to both $w_0$ and $w_a$.
So we expect these two parameters effectively constrained by our method.

@@

\section{Methodology}
The spectroscopic galaxy sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
the LOWZ sample, designed as an extension of the SDSS-I/II luminous red galaxy sample to $z\approx 0.4$ and fainter luminosities,
and the CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$),
targeted to be an approximately stellar mass limited sample of massive, luminous galaxies \cite{Reidetal:2016}.
In the clustering analysis we use 1,133,326 galaxies, split into six, non-overlapping redshift bins, 
$0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
The number density of galaxies and the redshift binning scheme is plotted in the left panel of Fig.\ref{fig_TpCF}.

@@

@@

The right panel of Fig.\ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
The contour lines are not horizontal due to the effects of peculiar velocity,
and the RSD effect clearly manifest itself through the tilting of contour lines.
However, the shape of the tilted lines remain similar at different redshifts, a fact that enables us  to mitigate the RSD effect by focusing on the redshift dependence of the anisotropic clustering signal.
The ``correct'' cosmological model is selected by minimizing the amount of redshift evolution of $\hat\xi_{\Delta s}$,
via a $\chi^2$ function of 
\begin{equation}
 \chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2})
\end{equation}
where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering with respect to the lowest redshift bin,
while subtracting systematic effects:
\begin{eqnarray}
 {\bf p}(z_i,\mu_{j}) \equiv\ & \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right] \\ \nonumber
 &- \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}.
\end{eqnarray}
We use a number of $n_{\mu}$=20, 21, ... 25 bins for the value of $\hat\xi_{\Delta s}(\mu)$ at $0<\mu<\mu_{\rm max}$.
For the removal of fiber collision and the strong FoG effect near the LOS we take a cut $\mu_{\rm max} = 0.97$.

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_con}
   Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.
   Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
   %Results are consistent with $\Lambda$CDM.
   The constrained area is significantly reduced after combined with the AP method.
   %This shows the power of the AP method in constraining dynamical dark energy.
   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
   Right panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
   Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
   }
\end{figure*}

@@

@@

In detail, the number of pairs are only counted in a fiducial cosmology
-- which is taken as the $\Omega_m=0.26$ $\Lambda$CDM --
and ``translated'' to the measurements in a ``target'' cosmology using the relations, 
\begin{eqnarray}\label{eq:smumap}
 s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}^2+\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}, \\
 \mu_{\rm target} = \mu_{\rm fiducial} \frac{\alpha_\parallel}
 {\sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}^2 +\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}}
\end{eqnarray}
where $\alpha_{\bot}\equiv D_{A,\rm target}/D_{A,\rm fiducial}$,
$\alpha_{\parallel}\equiv H_{\rm fiducial}/H_{\rm target}$.
and values of $D_A$ and $H$ are computed in the effective redshifts of the six redshift bins.
%The left panel of Figure \ref{fig_method} shows how 
%$\xi(s,\mu)$ is mapped from the fiducial cosmology to another cosmology using the above relations.
In the fiducial cosmology
we measure $\xi(s,\mu)$ with a high resolution of
$\Delta s = 0.2 {\rm Mpc/h}$, $\Delta \mu = 1/600$,
%Let us call this ``approximate 2pCF'' method.
%to obtain the accurate number counts 
and these small ``pixels'' are grouped to infer 
the number counts in other cosmologies, 
in large pixels of $\Delta s = 1 {\rm Mpc/h}$, $\Delta \mu = 1/120$.
%in the fiducial cosmology and group the bins in the target cosmology.
In the case when one small pixel belongs to more than one larger pixel,
a correction is applied by computing the fraction of the overlapping area.
%\footnote{A dense grid can effectively reduce the ``edge effect'' produced when we map $\xi(s,\mu)$ from one cosmology to another.
%The edge effect would introduce artificial correlations between nearby pixels, smooth $\xi(s,\mu)$ a little bit, 
%reduce the value of $\chi^2$, and change the obtained cosmological constriants.
%We found that, using $\Delta s = 1 {\rm Mpc/h}$ and $\Delta \mu = 1/120$, 
%the cosmological constraints of \cite{Li2016} can not be properly reproduced.}.

We found when using the approximate method the computed 
$\hat\xi_{\Delta s}(\mu)$ in a non-fiducial cosmology suffers from
an error of $\lesssim0.5\%$, which is 10 times smaller than the statistical noise.
We checked that the approximate method can reproduce the results presented in \cite{Li2016} quite well.
% We checked that the approximate method can reproduce the results of precise method quite well.
% The right panel of Figure \cite{fig_method} shows the  $\Omega_m$-$w_0$ constraints obtained 
%  using the precise and approximate 2pCFs (here we fix $w_a=0$). 
%  They agree with each other quite well.

\begin{figure*}
   \centering{
   \includegraphics[width=6cm]{fig_smu.eps}
   \includegraphics[width=10.5cm]{fig_comp.eps}
   }
   \caption{\label{fig_method}
   Left panel: Mapping $\xi(s,\mu)$ from the fiducial cosmology to four other cosmologies. 
 The number counts are measured in the fiducial cosmology in the blue dashed grid (for illustration purpose 
  the grid shown here is much sparser than the grid adopted in real analysis).
 In the four cosmologies with $(\Omega_m,w) = (0.31,-1.5),\ (0.31,-0.5),\ (0.41,-1.0)\ \rm and\ (0.21,-1.0)$, 
 %due to the distortion of geometry,
 the distribution of number counts in $(s, \mu)$ space becomes the red solid grid.
 We utilize the mapping realtion to infer the 2pCFs in vaiours cosmologies without re-conducting the 2pCF statistics. 
 Right panel: Cosmological constraints in the $\Omega_m$-$w_0$ plane, with the value of $w_a$ fixed as zero.
 Results obtained using the precise 2pCFs (gray filled) 
 and approximate 2pCFs (blue solid) 2pCFs agree with each other quite well.
   }
\end{figure*}

@@

\section{Result}

@@

We performed a test of all the possible variables in our methodology.
Fig.\ref{fig_contest} shows that 
the result is unaffected by the line-of-sight $\mu$-cut, 
the number of angular bins, 
the range of radial integration and the choice of fiducial cosmology. 
%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
%decrease the number of angular bins to $n_{\mu}=15-20$,
%change the range of clustering to $8-30 \rm Mpc/h$,
%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
%exclude 1 or 2 high redshift bins,
%or reduce the number of mocks to 1000.
The result does not change significantly if we remove the highest redshift bin,
where the estimated systematics is comparably large.
The most striking point to note in our test is that the 
shift in contour position is not significant even when %we do not include the systematic correction.
the systematics are not corrected.
%This is reassuring, since we may have worried that {\it cosmological dependence} 
%of the systematic correction could influence the final result. 
This indicates that, for the data analysis of current galaxy surveys,
the systematic effects in our method may not be important.
But it remains to be seen if this is true for future galaxy surveys,
or when the cosmology dependence of the systematics effects is taken into account.

>>>>

%\altaffiltext{1}{xiaodongli@kias.re.kr}
%\altaffiltext{2}{cbp@kias.re.kr}
%\altaffiltext{3}{csabiu@kasi.re.kr}
%\altaffiltext{4}{\bf Hyunbae: your email}
%\altaffiltext{1}{Corresponding Author: kjhan@kias.re.kr}

@@

\begin{abstract}
We use the anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
%Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
%while improving upon earlier works \citep{Li2016},
%we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
%This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
%allowing for competitive and unbiased constrains to be placed on cosmological parameters.
The Alcock-Paczynski (AP) test was performed via the redshift dependence of clustering on scales of 6--40 $h^{-1}\rm Mpc$.
We improve the methodology of \cite{Li2016} by significantly reducing its computation time. 
This enables us to efficiently explore three or more cosmological parameters.
We then apply the improved method on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$.
In combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, we obtain
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results 
reduces the error bars by $\sim$30-40\%,
%and reduces the area of $w_0-w_a$ contour by 50\%.
and improves the dark energy figure of merit by a factor of 2. 
We checked the robustness of the results.
%The AP method may %be combined with the standard BAO method,
%greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

@@

\begin{figure*}
   \centering{
   \includegraphics[height=5cm]{fig_xy.eps}
   %\includegraphics[height=8cm]{fig4_1.eps}
   %\includegraphics[height=7cm]{FVol.eps}
   %\includegraphics[height=8cm]{xy.eps}
   %\includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_xy}
   The distance dependence of the shape distortion in four wrongly assumed cosmologies.
   Assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
   There are four perfect squares with their true shapes plotted in blue dashed lines.
   They are measured by an observer located at the origin, and the distances are reprojected in the four wrong cosmologies.
   The apparently distorted shapes are plotted in red solid lines.
   }
\end{figure*}

@@

In recent years the Alcock-Paczynski (AP) test \citep{AP1979} applied to galaxy redshift samples \citep{Outram2004,Blake2011,Alam2016}, 
has allowed tight constraints to be placed on the background averaged distance scales, $D_A(z)$ and $H^{-1}(z)$.  
Assuming an incorrect cosmological model for the coordinate transformation between redshift space and comoving space
produces residual geometric distortions in the resultant galaxy distribution (see  Figure \ref{fig_xy}). 
These distortions are induced by the fact that measured distances along 
and perpendicular to the line of sight are connected with cosmological parameters differently. 
Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.

@@

Previously, we proposed to use the {\it redshift dependence} of the AP distortion\cite{Li2014} as a way of mitigating the RSD effect. The clustering anisotropies produced by RSD are, although large, close to uniform in magnitude over a wide range in redshift.  However, if cosmological parameters are incorrectly chosen resulting in an AP effect, 
the anisotropy in the clustering signal has a clear redshift dependence
(as an illustration, Figure \ref{fig_xy} shows how the shape distortion of objects varies with distance (i.e., redshift) 
when incorrect cosmologies are used to infer distances).
In a later work\cite{Li2015}, we developed an AP methodology 
that utilizes the redshift dependence of the galaxy 2-point correlation function (2pCF), 
measured as a function of angle between the galaxy pair and line-of-sight (LoS).

@@

The CPL parametrization has many obvious advantages, for instance, a manageable parameter space, 
the bounded behavior at high redshift, 
and the ability to accurately reconstruct many dark energy theories\cite{CPL_L}. 
So it was widely used in the literature to reconstruct dark energy from observations.
The constraining power is usually quantified by the DETF (Dark Energy Task Force) \cite{DETF} figure of merit, 
defined as the reciprocal of the area of the error ellipse enclosing the 95\% confidence limit (CL) in the $w_0-w_a$ plane. 
Figure \ref{fig_xy} shows that redshift dependence of shape distortion is sensitive to both $w_0$ and $w_a$.
So we expect these two parameters effectively constrained by our method.

@@

\section{Methodology}

\subsection{Quantifying the redshift dependece of AP distortion}

The spectroscopic galaxy sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
the LOWZ sample, designed as an extension of the SDSS-I/II luminous red galaxy sample to $z\approx 0.4$ and fainter luminosities,
and the CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$),
targeted to be an approximately stellar mass limited sample of massive, luminous galaxies \cite{Reidetal:2016}.
In the clustering analysis we use 1,133,326 galaxies, split into six, non-overlapping redshift bins, 
$0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
The number density of galaxies and the redshift binning scheme is plotted in the left panel of Figure \ref{fig_TpCF}.

@@

\begin{figure*}
   \centering{
   \includegraphics[width=16cm]{fig_smu.eps}
%   \includegraphics[width=10.5cm]{fig_comp.eps}
   }
   \caption{\label{fig_method}
   Mapping $\xi(s,\mu)$ from the fiducial cosmology (taken as the $\Omega_m=0.26$ $\Lambda$CDM cosmology) to other cosmologies. 
 The number counts are measured in the fiducial cosmology in the blue dashed grid.
 In the four cosmologies with $(w_0,w_a) = (-1.5,0),\ (-0.5,0),\ (-1,2)\ \rm and\ (-1,-2)$,
 %due to the distortion of geometry,
 according to Equation \ref{eq:smumap},
 the distribution of measured number counts in $(s, \mu)$ space becomes the red solid grid,
 To ensure the accuracy, we count the number of pairs in 5 times smaller pixels (the small red pixels), 
 and group them together to infer the values of $\xi(s, \mu)$ in blue dashed grid.
 For illustration purpose, 
  the blue and red grids are all 10 times sparser than the grids adopted in real analysis.
}
\end{figure*}

\begin{figure*}
   \centering{
   \includegraphics[width=8.5cm]{fig_comp.eps}
   \includegraphics[width=8.5cm]{fig_IO.eps}
   }
   \caption{\label{fig_Check}
 Left panel: Cosmological constraints from the BOSS DR12 galaxies, in the $\Omega_m$-$w_0$ plane. 
 The value of $w_a$ is fixed as zero.
 Results obtained using the precise 2pCFs (cyan filled) 
 and approximate 2pCFs (blue solid) agree with each other quite well.
 Right panel: Input-output test of the methodology using four sets of HR4 mock catalogues.
 The approximate 2pCFs are used in the analysis.
 The simulation cosmology, $\Omega_m=0.26$ $\Lambda$CDM, is marked by the black plus.
 The inferred cosmological constraints from the method, shown in the cygan contours, are consistent with the input cosmology.
   }
\end{figure*}

@@

The right panel of Figure \ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
The contour lines are not horizontal due to the effects of peculiar velocity,
and the RSD effect clearly manifest itself through the tilting of contour lines.
However, the shape of the tilted lines remain similar at different redshifts, a fact that enables us  to mitigate the RSD effect by focusing on the redshift dependence of the anisotropic clustering signal.
The ``correct'' cosmological model is selected by minimizing the amount of redshift evolution of $\hat\xi_{\Delta s}$,
via a $\chi^2$ function of 
\begin{equation}
 \chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2})
\end{equation}
where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering with respect to the lowest redshift bin,
while subtracting systematic effects:
\begin{eqnarray}
 {\bf p}(z_i,\mu_{j}) \equiv\ & \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right] \\ \nonumber
 &- \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}.
\end{eqnarray}
We use a number of $n_{\mu}$=20, 21, ... 25 bins for the value of $\hat\xi_{\Delta s}(\mu)$ at $0<\mu<\mu_{\rm max}$.
For the removal of fiber collision and the strong FoG effect near the LOS we take a cut $\mu_{\rm max} = 0.97$.

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[width=8cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
   \includegraphics[width=8cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_con}
   Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.
   Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
   %Results are consistent with $\Lambda$CDM.
   The constrained area is significantly reduced after combined with the AP method.
   %This shows the power of the AP method in constraining dynamical dark energy.
   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
   Right panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
   Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
   }
\end{figure*}

@@

\subsection{Approximating the 2pCFs in cosmologies other than the fiducial one}

@@

In detail, the number of pairs are only counted in a fiducial cosmology
-- which is taken as the $\Omega_m=0.26$ $\Lambda$CDM --
and ``translated'' to the measurements in a ``target'' cosmology using the relations, 
\begin{eqnarray}\label{eq:smumap}
 s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}^2+\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}, \\
 \mu_{\rm target} = \mu_{\rm fiducial} \frac{\alpha_\parallel}
 {\sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}^2 +\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}}
\end{eqnarray}
where $\alpha_{\bot}\equiv D_{A,\rm target}/D_{A,\rm fiducial}$,
$\alpha_{\parallel}\equiv H_{\rm fiducial}/H_{\rm target}$.
and values of $D_A$ and $H$ are computed in the effective redshifts of the six redshift bins.
In the fiducial cosmology
we measure $\xi(s,\mu)$ with a high resolution of
$\Delta s = 0.2 {\rm Mpc/h}$, $\Delta \mu = 1/600$,
%Let us call this ``approximate 2pCF'' method.
%to obtain the accurate number counts 
and these small ``pixels'' are grouped to infer 
the number counts in other cosmologies, 
in large pixels of $\Delta s = 1 {\rm Mpc/h}$, $\Delta \mu = 1/120$.
In the case when one small pixel belongs to more than one larger pixel,
a correction is applied by computing the fraction of the overlapping area.
%in the fiducial cosmology and group the bins in the target cosmology.
%\footnote{A dense grid can effectively reduce the ``edge effect'' produced when we map $\xi(s,\mu)$ from one cosmology to another.
%The edge effect would introduce artificial correlations between nearby pixels, smooth $\xi(s,\mu)$ a little bit, 
%reduce the value of $\chi^2$, and change the obtained cosmological constriants.
%We found that, using $\Delta s = 1 {\rm Mpc/h}$ and $\Delta \mu = 1/120$, 
%the cosmological constraints of \cite{Li2016} can not be properly reproduced.}.

The above procedure is illustrated in Figure \ref{fig_method}.
Using the relations given by Equation \ref{eq:smumap},
we obtained the distribution of number counts in cosmologies other than the fiducial cosmology.
To ensure the accuracy of mapping, the number counting is conducted using 5 times smaller pixels (the small red pixels), 
and grouped together to infer the number counts in the standard resolution (the large blue dashed pixels).

%We checked that the approximate method can reproduce the results presented in \cite{Li2016} quite well.

The approximation procedure only introduces a $\lesssim0.5\%$ error in the $\hat\xi_{\Delta s}(\mu)$, 
which is 10 times smaller than the noise of $\hat\xi_{\Delta s}(\mu)$.
We checked that the approximate method can reproduce the results of precise method quite well.
The left panel of Figure \ref{fig_Check} shows the  $\Omega_m$-$w_0$ constraints obtained 
  using the precise and approximate 2pCFs (here we fix $w_a=0$). 
They agree with each other quite well.

To further check the robustness of the approximate method, 
we did an input-output test using the four sets of HR4 mock catalogues \cite{HR4}.
The results are shown in the right panel of Figure \ref{fig_Check}. 
The input cosmology is the simulation cosmology, i.e. $\Omega_m=0.26$ $\Lambda$CDM.
It lies within the 1$\sigma$ conour of the inferred constraints.

@@

\section{Results}

@@

We performed a test of all the possible variables in our methodology.
Fig.\ref{fig_contest} shows that 
the result is unaffected by the line-of-sight $\mu$-cut, 
the number of angular bins, 
the range of radial integration and the choice of fiducial cosmology. 
%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
%decrease the number of angular bins to $n_{\mu}=15-20$,
%change the range of clustering to $8-30 \rm Mpc/h$,
%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
%exclude 1 or 2 high redshift bins,
%or reduce the number of mocks to 1000.
The result does not change significantly if we remove the highest redshift bin,
where the estimated systematics is comparably large.
The most striking point to note in our test is that the 
shift in contour position is not significant even when %we do not include the systematic correction.
the systematics are not corrected.
%This is reassuring, since we may have worried that {\it cosmological dependence} 
%of the systematic correction could influence the final result. 
%This suggest that the CPL constraints reported are robust.
This indicates that, for the data analysis of current galaxy surveys,
the systematic effects in our method may not be important.
But it remains to be seen if this is true for future galaxy surveys,
or when the cosmology dependence of the systematics effects is taken into account.
